Prefetching SPARQL query cacher

### 2016-06-05 dissertation/cache-proxy.tex
minor
clarify

The system is in the convergence of the directions described in this
dissertation: It should relieve the remote endpoint of some of the
burden to evaluated the query and it should add to the robustness of the
open Web SPARQL infrastructure. It uses hypermedia to answer individual
triple patterns, based on Triple Pattern Fragments  \cite{ldf1}. The
system can only answer triple patterns, but other than that, supports
SPARQL 1.1 in its entirety. This was made possible to develop quickly
by the efforts put into the query planning in the Attean framework
described in Section~\ref{sec:conpush}. Caching based on RFC7234
\cite{rfc7234} was shown to be of possible use in the survey I
conducted. Finally, it was planned to be evaluated using
Design of Experiments.

@@

My interest is the case where the caching proxy has no further
knowledge of the data than what is exposed through the SPARQL Endpoint
or hypermedia metadata. While this would be known as a mediator in the
database literature and has also been a field of study for 20 years, I
focus on a practical motivation stemming mainly from what is currently
available, and in practice, there is very little information. Also,
this study is also practically restricted to HTTP. If the cache is to
be shared, then it would typically reside on the forward proxy, or in
a CDN.

@@

Thus, the main contribution from this project is the remarkable ease
with which it was implemented.

>>>>

The system is in the convergence of the directions described in this
dissertation: It should relieve the remote endpoint of some of the
burden to evaluate the query and it should add to the robustness of the
open Web SPARQL infrastructure. It uses hypermedia to answer individual
triple patterns, based on Triple Pattern Fragments  \cite{ldf1}. The
system can only answer triple patterns, but other than that, supports
SPARQL 1.1 in its entirety. This was made possible to develop quickly
by the efforts put into the query planning in the Attean framework
described in Section~\ref{sec:conpush}. Caching based on RFC7234
\cite{rfc7234} was shown to be of possible use in the survey I
conducted. Finally, it was planned to be evaluated using
Design of Experiments.

@@

My interest is the case where the caching proxy has no further
knowledge of the data than what is exposed through the SPARQL Endpoint
or hypermedia metadata. While this would be known as a mediator in the
database literature and has also been a field of study for 20 years, I
focus on a practical motivation stemming mainly from what is currently
available. In current practice, very little information is available
to the mediator. Also, this study is also practically restricted to
HTTP. If the cache is to be shared, then it would typically reside on
the forward proxy, or in a CDN.

@@

Thus, the main contribution from this project is the ease
with which it was implemented.
